Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-01-14 Supplemental-Material-B-Annotated-Analysis.Rmd
worker ols regression adjusted

#### ML regression

@@

@@

@@

```{r workerFreqQualCor}
# prepare data
workerAvFreQual <- dtWorker$full %>%
  group_by(ExternalReference) %>%
  summarise(
    n = n(),
    SumContactNL = sum(Contact_dum),
    PercContactNL = SumContactNL / n * 100,
    SumContactNLAll = sum(number),
    AvAttitude = mean(thermometerDutch_1, na.rm = TRUE),
    AvQuality = mean(quality_overall_1, na.rm = TRUE)
  ) %>%
  mutate(
    WinSumContactNL = DescTools::Winsorize(SumContactNL),
    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
  )

```{r workerModelOlsAttFreqQual}
# regression
mdlWorker$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL * AvQuality, data = workerAvFreQual)
# summary(lmWorkerAttFreqQualX)

interactions::interact_plot(
  mdlWorker$lmAttFreqQualX,
  pred = AvQuality,
  modx = SumContactNL,
  interval = TRUE,
  partial.residuals = TRUE
)

interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
                             pred = AvQuality,
                             modx = SumContactNL,
                             alpha = .05)
```

>>>>

In a next step we check whether the effect of outgroup interactions, in part, depends on the quality during the interactions. In this step we aggregate the within person data to remove any dependency issues. Additionally, because we can only assess interaction quality when there is an interaction, it is difficult to assess this with the interaction dummy as a within person predictor. Instead, we will use an aggregate measure of interaction quality and average interaction quality to consider the two predictors jointly.  Such an aggregation in essence mirrors the general 'past recall' approach that dominates the field. The only difference being that we aggregate data that participants recorded shortly after the actual interactions, wheras in most recall studies this aggregation is done mentally by the participant.

```{r workerFreqQualCor}
# prepare data
workerAvFreQual <- dtWorker$full %>%
  group_by(ExternalReference) %>%
  summarise(
    n = n(),
    SumContactNL = sum(Contact_dum),
    PercContactNL = SumContactNL / n * 100,
    SumContactNLAll = sum(number),
    AvAttitude = mean(thermometerDutch_1, na.rm = TRUE),
    AvQuality = mean(quality_overall_1, na.rm = TRUE)
  ) %>%
  mutate(
    WinSumContactNL = DescTools::Winsorize(SumContactNL),
    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll),
    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
  )

```{r workerModelOlsAttFreqQual}
# regression
mdlWorker$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = workerAvFreQual)
# summary(lmWorkerAttFreqQualX)

interactions::interact_plot(
  mdlWorker$lmAttFreqQualX,
  pred = AvQuality_c,
  modx = SumContactNL_c,
  interval = TRUE,
  partial.residuals = TRUE
)

interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
                             pred = AvQuality_c,
                             modx = SumContactNL_c,
                             alpha = .05)
```

### ML regression

@@

#### Unconditional model

@@

#### random intercept with predictors

@@
